Scalar Feedback based Joint Time-Frequency Precoder interpolation for MIMO-OFDM Systems

### 2019-10-15 paper/main.tex
Add more changes

For the adaptive channel tracking scheme, the arrows in
Fig.~\ref{fig:adpm-fig} show how previous quantized values along with
the 1-bit enhancement are used to find the new quantized value. Since
we use a single bit adaptation, the amount of feedback required is 1
bit for each scalar parameter that is being tracked. On an average,
this can be reduced by half if we transmit only $\Theta$ values for
one-time instance and only $\Phi$ values for the next time instant in
an alternating fashion (the untransmitted value is assumed to be the
same as that at the previous instant). In this case, the average
number of bits required to quantize a channel matrix will be
$N_{T}(2N_{T} - N_{R})/2$.

One issue that is associated with the tracking the $\phi_i$ parameters
is that they may change abruptly (cite the figure) between $-\pi$ and
$\pi$ due to jumps of $2\pi$. We have avoided this by unwrapping the
phases to facilitate continuous tracking.
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$. To construct the rest of the subcarriers, we will use
precoder parameters from both the past and future and time instances
to do the interpolation (using backtracking to ensure causality). In
Fig.~\ref{fig:adpm-fig}, each parameter is interpolated using the
neighbouring subcarriers using bilinear interpolation (equivalent to
linear interpolation in two dimensions). These interpolated values and
then used to reconstruct the precoding matrices all together. Thus,
the approach here is able to exploit the time and frequency
correlation jointly to enhance performance.

>>>>

For the adaptive channel tracking scheme, the arrows in
Fig.~\ref{fig:adpm-fig} show how previous quantized values along with
the 1-bit enhancement are used to find the new quantized value. Since
we use a single bit adaptation, the amount of feedback required is 1
bit for each scalar parameter that is being tracked. On average, this
can be reduced by half if we transmit only $\Theta$ values for
one-time instance and only $\Phi$ values for the next time instant in
an alternating fashion (the untransmitted value is assumed to be the
same as that at the previous instant). In this case, the average
number of bits required to quantize a channel matrix will be
$N_{T}(2N_{T} - N_{R})/2$.

One issue that is associated with the tracking the $\phi_i$ parameters
is that they may change abruptly between $-\pi$ and
$\pi$ due to jumps of $2\pi$. We have avoided this by unwrapping the
phases to facilitate continuous tracking.
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$. To construct the rest of the subcarriers, we will use
precoder parameters from both the past and future and time instances
to do the interpolation (using backtracking to ensure causality). In
Fig.~\ref{fig:adpm-fig}, each parameter is interpolated using the
neighbouring subcarriers using bilinear interpolation (equivalent to
linear interpolation in two dimensions). These interpolated values and
then used to reconstruct the precoding matrices all together. Thus,
the approach here is able to exploit the time and frequency
correlation jointly to enhance performance.
